Calculating Entropies With Nested Sampling

### 2017-01-15 paper/ms.tex
Why it's hard
Distinguish the two kinds of conditional entropy

The

@@

>>>>

This is difficult to compute because the expression
for the posterior distribution
\begin{align}
p(\x | \d) &= \frac{p(\x)p(\d | \x)}{p(\d)}
\end{align}
contains the marginal likelihood $p(\d)$.

It is important to distinguish between $H_{\x | \d}$ and the
entropy of $\x$ given a particular value of $\d$, which might be written
$H_{\x | \d=\d_0}$.
The former measures the degree to which one question answers
another, so is a function of two questions. The latter measures the
degree to which a {\em statement} answered a question, and is a function
of a question and a statement.

@@

The mutual information is
\begin{align}
I_{\x, \d} &= \sum_{\x} \sum_{\d}
\end{align}
